---
title: "Auto-numbering and cross-referencing of figures and tables in rmarkdown"
output: html_document
---

TODO: check this out: https://github.com/adletaw/captioner

Here's how to use:

1. Copy and paste the first two code chunks in this document to the top of your document
2. Make sure you have knitr and kfigr installed, use `devtools::install_github("github mkoohafkan/kfigr")` to install kfigr
3. For chunks in your doc that produce a figure or table for which you want a caption, be sure to include a label in the chuck options line. For example, the first chunk is this doc has the label `number_figures`
4. Also in the chunk options line, you need to specify the anchor type and the caption, for example `anchor="figure", fig.cap="Here is a nice figure"`, see the examples below. That will auto-generate the caption and give you auto-numering. See the example below for using with tables. 
5. When you want to refer to the figure or table in your text, use a bit of in-line code like so `r figr('my-label', TRUE, type="figure")` which will generate a cross-reference like 'figure 3' or whatever the correct number is for the figure produced by the chunk that has the label 'my-label'
6. Other similar methods:
    - http://rmflight.github.io/posts/2012/10/papersinRmd.html & https://gist.github.com/rmflight/3858973
    - http://galahad.well.ox.ac.uk/repro/
    - http://gforge.se/2014/01/fast-track-publishing-using-knitr-part-iii/
    

```{r number_figures, echo=FALSE}
# This is a knitr hook to enable figure and table captions
# number figures
# from http://stackoverflow.com/a/18672268/1036500
library("knitr")
tn = local({
  i = 0
  function(x) {
    i <<- i + 1
    paste("<table><caption>", 'Figure ', i, ': ', x, "</caption><colgroup><col width='100'></col></colgroup><thead><tr class='header'></tr></thead><tbody></tbody></table><p>", sep = '')
  }
})
knit_hooks$set(fig.cap = function(before, options, envir) {
  if(!before)
    tn(options$fig.cap)
})
default_output_hook = knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
  if (is.null(options$fig.cap) == F)  
    x
  else
    default_output_hook(x,options)
})

# number tables
# from http://stackoverflow.com/a/18672268/1036500
to = local({
  i = 0
  function(x) {
    i <<- i + 1
    paste("<table><caption>", 'Table ', i, ': ', x, "</caption><colgroup><col width='100'></col></colgroup><thead><tr class='header'></tr></thead><tbody></tbody></table><p>", sep = '')
  }
})
knit_hooks$set(tab.cap = function(before, options, envir) {
  if(!before)
    to(options$tab.cap)
})
default_output_hook = knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
  if (is.null(options$tab.cap) == F)  
    x
  else
    default_output_hook(x,options)
})
```

```{r setup, echo=FALSE, message=FALSE}
require(knitr)
require(kfigr) # devtools::install_github("github mkoohafkan/kfigr")
opts_chunk$set(message=FALSE, warning=FALSE)
```
# My document starts here

We can  embed plots, for example:

```{r first, anchor="figure", fig.cap="Rather small sample", fig.align='center'}
require(ggplot2)
qplot(rnorm(10), geom="histogram")
```

Note that for `r figr('first', TRUE, type="figure")` we can refer to the figure by the chunck label and that will generate an auto-numbered reference in the text that also links to the figure.

```{r second, anchor="figure", fig.cap="Look at this nice big sample", fig.align='center'}
require(ggplot2)
qplot(rnorm(1000), geom="histogram")
```

Note that for `r figr('second', TRUE, type="figure")` we can do the same thing, numbering is taken care of for us.


```{r mytable, anchor="table", tab.cap="my table about cars", tab.align='center'}
kable(mtcars)
```

And we can have a table, see `r figr('mytable', TRUE, type="table")` we can refer to the table with a numbered reference in the text that also links to the table.

We can refer to the figures and tables multiple times in the text with no problems: `r figr('first', TRUE, type="figure")`, `r figr('second', TRUE, type="figure")`, `r figr('mytable', TRUE, type="table")`



